### 2018-12-08 Sections/errors_in_quantum_networks.tex
Cat states, loss

Given that quantum communication links will typically be optical, the dominant error mechanism is likely to be loss. We let the efficiency, $\eta$, of an optical quantum process be the probability that a given photon entering the channel leaves the channel in the desired mode, or probability \mbox{$1-\eta$} of being lost. In the case of information encoded into single-photon states, e.g using the polarisation degree of freedom, $\eta$ corresponds exactly to the success probability of the communication.

When implementing protocols employing post-selection upon detecting all photons, the protocol will be non-deterministic, where loss dictates the protocol's success probability. Specifically, with $n$ photons, each with efficiency $\eta$, the net post-selection success probability of the entire device is $\eta^n$. This implies an exponential number of trials, \mbox{$(1/\eta)^n$}, is required in post-selected protocols. Clearly this exponential scaling is of concern, requiring demanding efficiencies in future large-scale implementations.

Formally, let $\mathcal{E}^\mathrm{loss}_\eta$ be the loss channel with efficiency $\eta$. The channel acting on an initially pure single-photon state, $\ket{1}$, can be modelled as a beamsplitter with transmissivity $\eta$ acting on the state, where the reflected mode is traced out, shown in Fig.\ref{fig:loss_model}. This yields the quantum process,
\begin{align}
\mathcal{E}^\mathrm{loss}_\eta(\hat\rho) = \mathrm{tr}_B[\hat{U}_\mathrm{BS}(\hat\rho_A\otimes\ket{0}_B\bra{0}_B)\hat{U}_\mathrm{BS}^\dag],
\end{align}
where $\hat{U}_\mathrm{BS}$ is the beamsplitter operation. In the special case of the vacuum and single-photon states, which is most relevant to qubit encodings, we obtain,
\begin{align}
	\mathcal{E}^\mathrm{loss}_\eta(\ket{0}\bra{0}) &= \ket{0}\bra{0}, \nonumber \\
\mathcal{E}^\mathrm{loss}_\eta(\ket{1}\bra{1}) &= (1-\eta)\ket{0}\bra{0} + \eta\ket{1}\bra{1}.
\end{align}
This dynamic is of the same form as amplitude damping (Sec.~\ref{sec:amp_damp}). In the general case of an $n$-photon Fock state, we obtain,
\begin{align}
	\mathcal{E}^\mathrm{loss}_\eta(\ket{n}\bra{n}) = \sum_{i=0}^n \binom{n}{i} \eta^i(1-\eta)^{n-i} \ket{i}\bra{i}.
\end{align}

@@

Consecutive loss channels act multiplicatively,
\begin{align}
\mathcal{E}_{\eta_1}^\mathrm{loss} \circ \mathcal{E}_{\eta_2}^\mathrm{loss} = \mathcal{E}_{\eta_1 \eta_2}^\mathrm{loss}.
\end{align}
In the special case of linear optics circuits, loss channels have the elegant property that, provided the loss rate is uniform across all modes, they can be commuted through the circuit to the front or back \cite{???}\index{Loss!Commutation}. Specifically,
\begin{align}
(\mathcal{E}_{\eta}^\mathrm{loss})^{\otimes m} \circ \mathcal{E}_U = \mathcal{E}_U \circ (\mathcal{E}_{\eta}^\mathrm{loss})^{\otimes m},
\end{align}
where $\mathcal{E}_U$ is a unitary linear optics process, implementing a photon-number-preserving map of the form of Eq.~(\ref{eq:LO_unitary_map}). This simplifies the treatment of distinct system inefficiencies (such as source, network and detector inefficiencies) by allowing us to commute them to the beginning or end of the circuit and combine them together into a single net efficiency. In many scenarios, this allows the different system inefficiencies to be dealt with via post-selection.

This process would apply equivalently to both horizontal and vertical polarisations. Therefore, via linearity, the loss channel acting on a polarisation-encoded qubit (Sec.~\ref{sec:single_phot_enc}) yields,
\begin{align}
\mathcal{E}^\mathrm{loss}_\eta(\ket\psi_\mathrm{pol}\bra\psi_\mathrm{pol}) = (1-\eta) \ket{0}\bra{0} + \eta\ket\psi_\mathrm{pol}\bra\psi_\mathrm{pol}.
\end{align}
The same applies in the context of dual-rail encoding. Note that while this transformation mixes the state in the photon-number degree of freedom, it preserves coherence between the horizontal and vertical single-photon components. Thus, upon successful post-selection, the state is projected back onto the desired qubit state.

@@

@@

@@

@@

The scaling of loss over distance $d$ varies depending on the medium through which the light traverses. When propagating through fibre, atmosphere, or some other lossy medium, net efficiency scales inverse exponentially as,
\begin{align}
	\eta = O(e^{-\alpha d}),
\end{align}
where $\alpha$ is a characteristic of the medium\footnote{With present-day fibre technology, this characteristic decay rate is on the order of \mbox{$\alpha = \frac{1}{22\mathrm{km}}$}.}. In space on the other hand, where the medium of propagation is vacuum, which is effectively lossless, the effective loss rate is not determined by the medium, but rather by the fact that the spot-size\index{Spot-size} of an optical state is subject to dispersion\index{Dispersion} and grows only quadratically with distance, as shown in Fig.~\ref{fig:free_space_disp}. Then when the light is detected, if the spot-size is greater than the detector aperture, the undetected component effectively translates to loss. Thus through free-space the effective efficiency scales as,
\begin{align}
	\eta = O\left(\frac{1}{d^2}\right),
\end{align}
which is far more favourable than the exponential scaling inherent to lossy mediums. This provides space-based quantum networks with an inherent competitive advantage compared to any form of ground-based network.

@@

The dephasing error model describes the deterioration of quantum coherence in a state. It does not change the actual amplitudes of the components in the superposition, but rather reduces the state to a mixture of those components. Thus, dephasing can be thought of as destroying quantum information (coherence), while retaining classical information (probability amplitudes). In terms of qubits, dephasing is most commonly represented using the Kraus representation,
\begin{align} \label{eq:dephasing_channel}
\mathcal{E}_p^\mathrm{dephasing}(\hat\rho) = p\cdot\hat\rho + (1-p)\cdot \hat{Z}\hat\rho\hat{Z},
\end{align}
where $\hat\rho$ is the state of a single qubit, and $\hat{Z}$ is the Pauli phase-flip operator\footnote{Bit-flip\index{Bit-flip!Channel} and bit-phase-flip\index{Bit-phase-flip channel} channels may be represented similarly by replacing $\hat{Z}$ with $\hat{X}$ or $\hat{Y}$ respectively, although these don't arise as naturally as dephasing in many physical contexts.}. Intuitively this tells us that the dephasing channel creates a mixture of an input state with its phase-flipped self.

@@

A qubit dephasing channel is often quoted in terms of its $T_2$-time\index{T$_2$-time}, a characteristic time for dephasing to occur under continuous time-evolution. Specifically, the probability of no dephasing occurring scales as,
\begin{align}
p_\mathrm{no\,error} = e^{-t/T_2},	
\end{align}
yielding a the equivalent dephasing channel,
\begin{align}
\mathcal{E}_t^\mathrm{dephasing}(\hat\rho) = e^{-t/T_2} \hat\rho + \frac{1}{2}(1-e^{-t/T_2})(\hat\rho + \hat{Z}\hat\rho\hat{Z}),
\end{align}
as shown in Fig.~\ref{fig:T2_time}. This is equivalent to adding a factor of $e^{-t/T_2}$ to the two off-diagonal (coherence) elements of a qubit's density matrix,
\begin{align}
	\hat\rho_t = \left(\begin{matrix}{}
 \alpha & e^{-t/T_2}\gamma \\
 e^{-t/T_2}\gamma^* & \beta
\end{matrix}\right).
\end{align}

@@

@@

The degree of amplitude damping is often quoted in terms of a channel's $T_1$-time\index{T$_1$-time}, characterising the expected time for the excited state to undergo spontaneous emission and relax to the ground state. Using this parameterisation we can express the amplitude damping channel as,
\begin{align}
\mathcal{E}_t^\mathrm{relax}(\hat\rho) = e^{-t/T_1}\hat\rho + (1-e^{-t/T_1})\ket{0}\bra{0},
\end{align}
for which the output state is of the form,
\begin{align}
\hat\rho_t = \left(\begin{matrix}{}
1 + (\alpha-1) e^{-t/T_1} & \gamma e^{-t/T_1} \\
\gamma^* e^{-t/T_1} & \beta e^{-t/T_1}
\end{matrix}\right).
\end{align}

@@

>>>>

Given that quantum communication links will typically be optical, the dominant error mechanism is likely to be loss. We let the \textit{efficiency}, $\eta$, of an optical quantum process be the probability that a given photon entering the channel leaves the channel in the desired mode, or probability \mbox{$1-\eta$} of being lost. In the case of information encoded into single-photon states, e.g using the polarisation degree of freedom, $\eta$ corresponds exactly to the success probability of the communication.

When implementing protocols employing post-selection upon detecting all photons, the protocol will be non-deterministic, where loss dictates the protocol's success probability. Specifically, with $n$ photons, each with efficiency $\eta$, the net post-selection success probability\index{Post-selection success probability} of the entire device is,
\begin{align}
	P=\eta^n.
\end{align}
This implies an exponential number of trials\index{Trials},
\begin{align}
	N=\left(\frac{1}{\eta}\right)^n,
\end{align}
is required in post-selected protocols. Clearly this exponential scaling is of concern, requiring demanding efficiencies in future large-scale implementations.

% Model

\subsubsection{Model}\index{Loss model}

Formally, let $\mathcal{E}^\mathrm{loss}_\eta$ be the loss channel with efficiency $\eta$. The channel acting on an initially pure single-photon state, $\ket{1}$, can be modelled as a beamsplitter with transmissivity $\eta$ acting on the state, where the reflected mode is traced out, shown in Fig.\ref{fig:loss_model}. This yields the quantum process,
\begin{align}
\mathcal{E}^\mathrm{loss}_\eta(\hat\rho) = \mathrm{tr}_B[\hat{U}_\mathrm{BS}(\hat\rho_A\otimes\ket{0}_B\bra{0}_B)\hat{U}_\mathrm{BS}^\dag],
\end{align}
where $\hat{U}_\mathrm{BS}$ is the beamsplitter operation.

@@

Consecutive loss channels act multiplicatively,
\begin{align}
\mathcal{E}_{\eta_1}^\mathrm{loss} \circ \mathcal{E}_{\eta_2}^\mathrm{loss} = \mathcal{E}_{\eta_1 \eta_2}^\mathrm{loss}.
\end{align}

% Linear optics networks

\subsubsection{Linear optics networks}\index{Linear optics networks}

In the special case of linear optics circuits, loss channels have the elegant property that, provided the loss rate is uniform across all modes, they can be commuted through the circuit to the front or back \cite{???}\index{Loss!Commutation}. Specifically,
\begin{align}
(\mathcal{E}_{\eta}^\mathrm{loss})^{\otimes m} \circ \mathcal{E}_U = \mathcal{E}_U \circ (\mathcal{E}_{\eta}^\mathrm{loss})^{\otimes m},
\end{align}
where $\mathcal{E}_U$ is a unitary linear optics process, implementing a photon-number-preserving map of the form of Eq.~(\ref{eq:LO_unitary_map}). This simplifies the treatment of distinct system inefficiencies (such as source, network and detector inefficiencies) by allowing us to commute them to the beginning or end of the circuit and combine them together into a single net efficiency. In many scenarios, this allows the different system inefficiencies to be dealt with via post-selection.

% Single-photon encoding

\subsubsection{Single-photon encoding}\index{Single-photon encoding}

In the case of the vacuum and single-photon states, which is most common to qubit encodings, we obtain,
\begin{align}
	\mathcal{E}^\mathrm{loss}_\eta(\ket{0}\bra{0}) &= \ket{0}\bra{0}, \nonumber \\
\mathcal{E}^\mathrm{loss}_\eta(\ket{1}\bra{1}) &= (1-\eta)\ket{0}\bra{0} + \eta\ket{1}\bra{1}.
\end{align}
This dynamic is of the same form as amplitude damping (Sec.~\ref{sec:amp_damp}).

% Polarisation & dual-rail encoding

\subsubsection{Polarisation \& dual-rail encoding}\index{Polarisation encoding}\index{Dual-rail encoding}

This process would apply equivalently to both horizontal and vertical polarisations. Therefore, via linearity, the loss channel acting on a polarisation-encoded qubit (Sec.~\ref{sec:single_phot_enc}) yields,
\begin{align}
\mathcal{E}^\mathrm{loss}_\eta(\ket\psi_\mathrm{pol}\bra\psi_\mathrm{pol}) = (1-\eta) \ket{0}\bra{0} + \eta\ket\psi_\mathrm{pol}\bra\psi_\mathrm{pol}.
\end{align}

The same applies in the context of dual-rail encoding. Note that while this transformation mixes the state in the photon-number degree of freedom, it preserves coherence between the horizontal and vertical single-photon components. Thus, upon successful post-selection, the state is projected back onto the desired qubit state.

% Photon-number encoding

\subsubsection{Photon-number encoding}\index{Photon-number encoding}

In the general case of an $n$-photon Fock state, we obtain,
\begin{align}
	\mathcal{E}^\mathrm{loss}_\eta(\ket{n}\bra{n}) = \sum_{i=0}^n \binom{n}{i} \eta^i(1-\eta)^{n-i} \ket{i}\bra{i}.
\end{align}

@@

% Coherent state encoding

\subsubsection{Coherent state encoding}\index{Coherent state encoding}

@@

% Cat state encoding

\subsubsection{Cat state encoding}

@@

%Consider an even-parity cat state, as per Eq.~(\ref{eq:cat_state_enc}). Subjecting this to a loss channel yields the mixed state,
%\begin{align}
%&\hat\rho_\mathrm{loss} = \mathcal{E}_\eta^\mathrm{loss}(\ket{\mathrm{cat}_+(\alpha)}\bra{\mathrm{cat}_+(\alpha)}) = {\mathcal{N}_+}^2 \nonumber\\
%&\cdot (\ket{\eta\alpha}\bra{\eta\alpha} + \ket{\eta\alpha}\bra{-\eta\alpha} + \ket{-\eta\alpha}\bra{\eta\alpha}+\ket{-\eta\alpha}\bra{-\eta\alpha}),
%\end{align}
%which has purity,
%\begin{align}
%	\mathcal{P} &= \mathrm{tr}({\hat\rho_\mathrm{loss}}^2)\nonumber\\
%	&=
%\end{align}

%\comment{To do}

% NOON states

\subsubsection{NOON states}\index{NOON states}

@@

% Scaling

\subsubsection{Scaling}

The scaling of loss over distance $d$ varies depending on the medium through which the light traverses. We will consider two dominant mediums, most relevant to future quantum networking:
\begin{itemize}
	\item Optical fibre\index{Optical fibres}: mode geometry is well-preserved, but optical medium is intrinsically lossy.
	\item Free-space\index{Free-space}: mode geometry is subject to dispersion\index{Dispersion}, but the medium is either lossless (in vacuum), or very low-loss (in atmosphere).
\end{itemize}

When propagating through fibre (or atmosphere, or some other lossy medium) net efficiency scales inverse exponentially as,
\begin{align}
	\eta = O(e^{-\alpha d}),
\end{align}
where $\alpha$ is a characteristic of the medium\footnote{With present-day fibre technology, this characteristic decay rate is on the order of \mbox{$\alpha = \frac{1}{22\mathrm{km}}$}.}.

In free-space on the other hand, where the medium of propagation is vacuum, which is effectively lossless, the effective loss rate is not determined by the medium, but rather by the fact that the spot-size\index{Spot-size} of an optical state is subject to dispersion\index{Dispersion} and grows only quadratically with distance, as shown in Fig.~\ref{fig:free_space_disp}. Then when the light is detected, if the spot-size is greater than the detector aperture, the undetected component effectively translates to loss. Thus through free-space the effective efficiency scales as,
\begin{align}
	\eta = O\left(\frac{1}{d^2}\right),
\end{align}
which is far more favourable than the exponential scaling inherent to lossy mediums. This provides space-based quantum networks with an inherent competitive advantage compared to any form of ground-based network.

Through atmospheric channels we will have both dispersion and distance-dependent loss, yielding an effective loss rate given by the product of the two effects,
\begin{align}
	\eta = O\left(\frac{e^{-\alpha d}}{d^2}\right).
\end{align}

@@

The dephasing error model describes the deterioration of quantum coherence in a state. It does not change the actual amplitudes of the components in the superposition, but rather reduces the state to a mixture of those components. Thus, dephasing can be thought of as destroying quantum information (coherence), while retaining classical information (probability amplitudes).

% Qubits

\subsubsection{Qubits}

In terms of qubits, dephasing is most commonly represented using the Kraus representation\index{Kraus representation},
\begin{align} \label{eq:dephasing_channel}
\mathcal{E}_p^\mathrm{dephasing}(\hat\rho) = p\cdot\hat\rho + (1-p)\cdot \hat{Z}\hat\rho\hat{Z},
\end{align}
where $\hat\rho$ is the state of a single qubit, and $\hat{Z}$ is the Pauli phase-flip operator\footnote{Bit-flip\index{Bit-flip!Channel} and bit-phase-flip\index{Bit-phase-flip channel} channels may be represented similarly by replacing $\hat{Z}$ with $\hat{X}$ or $\hat{Y}$ respectively, although these don't arise as naturally as dephasing in many physical contexts.}. Intuitively this tells us that the dephasing channel creates a mixture of an input state with its phase-flipped self.

@@

% T_2-times

\subsubsection{$T_2$-times}\index{T$_2$-time}

A qubit dephasing channel is often quoted in terms of its $T_2$-time, a characteristic time for dephasing to occur under continuous time-evolution. Specifically, the probability of no dephasing occurring scales as,
\begin{align}
p_\mathrm{no\,error} = e^{-t/T_2},	
\end{align}
yielding a the equivalent dephasing channel,
\begin{align}
\mathcal{E}_t^\mathrm{dephasing}(\hat\rho) = e^{-t/T_2} \hat\rho + \frac{1}{2}(1-e^{-t/T_2})(\hat\rho + \hat{Z}\hat\rho\hat{Z}),
\end{align}
as shown in Fig.~\ref{fig:T2_time}. This is equivalent to adding a factor of $e^{-t/T_2}$ to the two off-diagonal (coherence) elements of a qubit's density matrix,
\begin{align}
	\hat\rho_t = \left(\begin{matrix}{}
 \alpha & e^{-t/T_2}\gamma \\
 e^{-t/T_2}\gamma^* & \beta
\end{matrix}\right).
\end{align}

@@

% Optical states

\subsubsection{Optical states}

@@

@@

% T_1-times

\subsubsection{$T_1$-times}\index{T$_1$-time}

The degree of amplitude damping is often quoted in terms of a channel's $T_1$-time, characterising the expected time for the excited state to undergo spontaneous emission and relax to the ground state. Using this parameterisation we can express the amplitude damping channel as,
\begin{align}
\mathcal{E}_t^\mathrm{relax}(\hat\rho) = e^{-t/T_1}\hat\rho + (1-e^{-t/T_1})\ket{0}\bra{0},
\end{align}
for which the output state is of the form,
\begin{align}
\hat\rho_t = \left(\begin{matrix}{}
1 + (\alpha-1) e^{-t/T_1} & \gamma e^{-t/T_1} \\
\gamma^* e^{-t/T_1} & \beta e^{-t/T_1}
\end{matrix}\right).
\end{align}

### 2018-12-08 Sections/optical_encoding_of_quantum_information.tex
Cat states, loss

By manipulating these parameters, information can be encoded into coherent states. We could, for example, define two coherent states of opposite phase to represent qubit basis states,
\begin{align}
\ket{0} &\equiv \ket{\alpha}, \nonumber \\
\ket{1} &\equiv \ket{-\alpha}.
\end{align}
Note, however, that this representation for qubits is only approximate, since the two basis states are not perfectly orthogonal,
\begin{align}
\braket{-\alpha|\alpha} = e^{-2|\alpha|^2},
\end{align}
which is non-zero for any finite $\alpha$, whereas for ideal qubits we require \mbox{$\braket{0|1} = 0$}. However, for large $\alpha$, $\ket{\pm\alpha}$ closely approximate orthogonality.

@@

Another type of CV state, which can in fact encode quantum information, is superpositions of coherent states (colloquially known as `cat' states), with the encoding \cite{???},
\begin{align}
\ket{0} &\equiv \frac{1}{\sqrt{2(1+e^{-2|\alpha|^2})}} (\ket{\alpha}+\ket{-\alpha}) \nonumber \\
&= \ket{\mathrm{cat}_+(\alpha)},\nonumber \\
\ket{1} &\equiv \frac{1}{\sqrt{2(1-e^{-2|\alpha|^2})}}(\ket{\alpha}-\ket{-\alpha}) \nonumber \\
&= \ket{\mathrm{cat}_-(\alpha)}.
\end{align}
These two basis states contain strictly even or odd photon-number terms respectively (i.e they have well-defined parity\index{Parity}), implying that, unlike coherent states, they are always orthogonal, regardless of amplitude,
\begin{align}
\braket{\mathrm{cat}_+(\alpha)|\mathrm{cat}_-(\alpha)} = 0 \,\,\forall\,\alpha,
\end{align}
making them directly appropriate for qubit encoding, even for weak coherent amplitudes.

Unfortunately, cat states are notoriously difficult to prepare, and extremely sensitive to loss (Sec.~\ref{sec:single_phot_enc}) and dephasing (Sec.~\ref{sec:dephasing_error}). This arises because loss of a single photon flips the parity of the state to an orthogonal one, meaning that as $\alpha$ increases, the state is exponentially more susceptible to decohering into a mixture of the logical basis states.

>>>>

By manipulating these parameters, information can be encoded into coherent states. We could, for example, define two coherent states of opposite phase to represent qubit basis states,
\begin{align}
\ket{0} &\equiv \ket{\alpha}, \nonumber \\
\ket{1} &\equiv \ket{-\alpha}.
\end{align}
Note, however, that this representation for qubits is only approximate, since coherent states are not orthogonal,
\begin{align}\label{eq:coh_st_overlap}
\braket{\alpha|\beta} &= e^{-\frac{1}{2}(|\alpha|^2+|\beta|^2-2\alpha^*\beta)}\nonumber\\
&\neq \delta(\alpha-\beta),	
\end{align}
thus the two logical basis states are not perfectly orthogonal,
\begin{align}
\braket{-\alpha|\alpha} = e^{-2|\alpha|^2},
\end{align}
which is non-zero for any finite $\alpha$, whereas for ideal qubits we require \mbox{$\braket{0|1} = 0$}. However, for large $\alpha$, $\ket{\pm\alpha}$ closely approximate orthogonality, allowing them to be used as qubits.

@@

Another type of CV state, which can in fact encode quantum information, is superpositions of coherent states (colloquially known as `cat' states), with the encoding \cite{bib:JeongRalph05},
\begin{align}\label{eq:cat_state_enc}
\ket{0}_L &\equiv \mathcal{N}_+ (\ket{\alpha}+\ket{-\alpha}) \nonumber \\
&= 2\mathcal{N}_+ e^{-\frac{|\alpha|^2}{2}} \sum_{n=0}^\infty \frac{\alpha^{2n}}{\sqrt{(2n)!}} \ket{2n}, \nonumber\\
&= \ket{\mathrm{cat}_+(\alpha)},\nonumber \\
\ket{1}_L &\equiv \mathcal{N}_- (\ket{\alpha}-\ket{-\alpha}) \nonumber \\
&= 2\mathcal{N}_- e^{-\frac{|\alpha|^2}{2}} \sum_{n=0}^\infty \frac{\alpha^{2n+1}}{\sqrt{(2n+1)!}} \ket{2n+1},\nonumber\\
&= \ket{\mathrm{cat}_-(\alpha)},
\end{align}
where the normalisation factors are,
\begin{align}
\mathcal{N}_\pm = \frac{1}{\sqrt{2(1\pm e^{-2|\alpha|^2})}},
\end{align}
which arise due to the non-orthogonality of coherent states, Eq.~(\ref{eq:coh_st_overlap}). These two basis states contain strictly even or odd photon-number terms respectively (i.e they have well-defined parity\index{Parity}), implying that, unlike coherent states, they are always orthogonal, regardless of amplitude,
\begin{align}
\braket{\mathrm{cat}_+(\alpha)|\mathrm{cat}_-(\alpha)} = 0 \,\,\forall\,\alpha,
\end{align}
making them directly appropriate for qubit encoding, even for weak coherent amplitudes.

Unfortunately, cat states are notoriously difficult to prepare, and extremely sensitive to loss (Sec.~\ref{sec:eff_err}) and dephasing (Sec.~\ref{sec:dephasing_error}). This arises because loss of a single photon flips the parity of the state to an orthogonal one, meaning that as $\alpha$ increases, the state is exponentially more susceptible to decohering into a mixture of the logical basis states.
